---
title: "Papers"
execute:
  echo: false
  message: false
  warning: false
page-layout: full
include-back-link: false
toc-location: right
cache: false
---

```{r setup}
source(here::here("papers", "_render.R"))
```

```{=html}
<div class="pub-search-wrap">
  <input type="search" id="pub-search" class="pub-search-input"
         placeholder="Search by author, title, or journal…"
         aria-label="Search publications">
  <span id="pub-search-count" class="pub-search-count"></span>
</div>
<p id="pub-no-results" style="display:none; color:#888; font-style:italic;">
  No papers match your search.
</p>
```

## Journal Articles

\* indicates trainee under my supervision or co-supervision.

```{r}
render_pub_list("ARTICLE")
```

## Book Chapters

```{r}
render_pub_list("INCOLLECTION")
```

## Media mentions
- Our recent [paper](https://www.tandfonline.com/doi/full/10.1080/13607863.2025.2473634) on loneliness led by my former PhD student [Robin Richardson](https://www.robinarichardson.com/) (co-supervised with Arijit Nandi) was covered in over [280 outlets](https://newsroom.taylorandfrancisgroup.com/study-middle-aged-americans-are-lonelier-than-adults-in-other-countries-age-groups/) such as *ABC News*, *CNN*, *New York Post*, and *Euro News*, 2025-04-22.
- Coverage by [*The Indian Express*](https://indianexpress.com/article/india/extreme-wet-conditions-linked-to-increase-in-suicides-in-rural-india-study-6601839/) and [*Forbes*](https://www.forbes.com/sites/dishashetty/2020/09/24/droughts-floods-linked-to-mental-health-finds-new-study/#6529641a10f4) on our recent paper investigating environmental conditions and suicide in India, 2020-09-19.
- [Report](https://www.theleafnews.com/news/do-fatal-car-crashes-actually-increase-on-420-not-so-fast-says-new-research-506836442.html) by *The Leaf News* on our [paper]({{< ref "/publication/harper-2019-ac/index.md" >}}) looking at the cannabis "holiday" on April 20 and fatal traffic crashes, 2019-03-07.
- Feature (and interview) on the [Smarter Choices for Better Health Initiative](https://www.eur.nl/en/news/even-netherlands-has-important-differences-between-health-poor-and-rich-we-would-decrease), 2018-11-26.
- Coverage of our [paper]({{< ref "/publication/riddell-2018-aa/index.md" >}}) on gun violence in US states by [CNN](https://www.cnn.com/2018/04/23/health/gun-deaths-in-men-by-state-study/index.html), 2018-04-23.
- NPR's *Hidden Brain* [story](https://www.tpr.org/post/hidden-brain-great-recession-deaths) on our [paper]({{< ref "/publication/strumpf-2017-aa/index.md" >}}) looking at the impact of recessions on mortality, 2018-01-16.
- PBS NewsHour [coverage](https://www.pbs.org/newshour/nation/click-it-or-ticket-seat-belt-laws) of our [work]({{< ref "/publication/harper-2017-ac/index.md" >}}) on seat belt laws and traffic crash mortality, 2017-04-30.

```{=html}
<script>
(function () {
  var input    = document.getElementById('pub-search');
  var countEl  = document.getElementById('pub-search-count');
  var noRes    = document.getElementById('pub-no-results');
  var total    = document.querySelectorAll('.pub-entry').length;

  function filter() {
    var q = input.value.trim().toLowerCase();
    var shown = 0;

    document.querySelectorAll('.pub-year-entries').forEach(function (block) {
      var blockVisible = false;
      block.querySelectorAll('.pub-entry').forEach(function (entry) {
        var match = q === '' || entry.textContent.toLowerCase().includes(q);
        entry.style.display = match ? '' : 'none';
        if (match) { shown++; blockVisible = true; }
      });
      // Hide the year block and its label if nothing in it matches
      block.style.display = blockVisible ? '' : 'none';
      var label = block.previousElementSibling;
      if (label && label.classList.contains('pub-year-label'))
        label.style.display = blockVisible ? '' : 'none';
    });

    countEl.textContent = (q && shown < total)
      ? 'Showing ' + shown + ' of ' + total + ' papers'
      : '';
    noRes.style.display = (q && shown === 0) ? '' : 'none';
  }

  input.addEventListener('input', filter);
})();
</script>
```
